More than one Author with different Affiliations

### 2012-04-22 paper/ms.tex
Use cool blackboard bold
Got rid of delta notation

\documentclass[letterpaper, 11pt]{article}
\usepackage{authblk}
\usepackage{graphicx} 
\usepackage{natbib}
\usepackage{amsmath}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(x, y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the true flux $F$ within a particular pixel is:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy
\label{pixel}
\end{eqnarray}
We observe $F_{\rm{pixel}}$ for many pixels, with noise added.

Combining Equations~\ref{blur} and~\ref{pixel} gives:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \,dx\,dy
\end{eqnarray}

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{authblk}	% For nice author-affil lists
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\appendix
\section{Pixel Convolved PSF}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(x, y)$ (assumed normalised to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-x', y-y')
g(x', y') \, dx' \, dy' \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation, such that
the true flux $F$ within a particular pixel is:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} f_{\rm blurred}(x, y) \,dx\,dy\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
We observe $F_{\rm{pixel}}$ for many pixels, with noise added.

Combining Equations~\ref{blur} and~\ref{pixel} gives:
\begin{eqnarray}
F_{\rm{pixel}} &=& \iint_{\rm{pixel}} \iint f_0(x-x', y-y')
g(x', y') \, dx' \, dy' \,dx\,dy
\end{eqnarray}
